\chapter*{Acknowledgments}

There are no proper words to convey my deep gratitude and respect for my thesis and research advisor, Prof. Roman Karasev, Moscow Insitute of Physics and Technology, Russian Federation. With his course in discrete geometry, he not only inculcated my interest in manifold learning, but has inspired me to become an independent researcher. He helped me realize the power of critical reasoning, simple, but concrete mathematical representation of idea and guidance to recover when my steps faltered. He taught me how to critically question thoughts and express ideas in simple but scientific way. His insightful thought-provoking comments and constructive criticisms at different stages of my research allowed me to stay focused to core of research ideas. I am grateful to him for holding me to a high research standard and enforcing strict validations for each research result, and thus teaching me how to do research.


There is no way to express how much it meant to me to have been a member and faculty of discrete mathematics department for all meaningful discussion on different plethora  of research topics. The brilliant friends, colleagues and and all the other current and former Lab graduates students and visitors that I know inspired me over my stay in Moscow. Also, thanks to active communities of Python and Matlab.

I would like to thank all the people associated with Department of Discrete Mathematics, fellow students and teachers who have been source of thoughts, inspiration and smiles. Acknowledgement will be incomplete without expressing sincere gratitude to Prof. Andrei Raigorodskii for providing excellent infrastructure, guidance and scholastic path to realize our dreams into reality.

Though only some name appears on the cover of this thesis, a great many people have contributed to its production. I owe my deep gratitude to all those people who have made this thesis possible and because of whom my graduate experience has been one that I will cherish forever. 

In conclusion, I recognize that this research would not have been possible without the financial assistance from Russian Government and MIPT, and express my gratitude to those agencies.
   
\begin{flushright}
Pankaj Kumar
\end{flushright}



