\begin{thebibliography}{99}
\setlength{\parskip}{1em}

\bibitem{Thor2009} Thorstensen, Nicolas. 
\newblock Manifold learning and applications to shape and image processing.
\newblock {\em PhD Thesis, Ecole des Ponts ParisTech}.
\newblock \url {https://pastel.archives-ouvertes.fr/pastel-00005860/file/Thesis.pdf}, 2009.


\bibitem{Tal2008} Talwalkar, A and Kumar, S and Rowley, H. 
\newblock Large-scale manifold learning.
\newblock {\em 2008 IEEE Conference on Computer Vision and Pattern Recognition}. 1-8, June, 2008.


\bibitem{Ety2008} Etyngier, Patrick . 
\newblock Statistical learning, Shape Manifolds and Applications to Image Segmentation.
\newblock {\em PhD thesis, Ecole Nationale des Ponts et Chausees}.
\newblock \url {http://imagine.enpc.fr/publications/papers/PhD08.pdf}, 9, 41, 135, 2008.

\bibitem{Bel2002} Belkin, Mikhail and Partha Niyogi. 
\newblock Laplacian Eigenmaps and Spectral Techniques for Embedding and Clustering.
\newblock {\em Advances in Neural Information Processing Systems 14}.
\newblock \url {http://papers.nips.cc/paper} MIT Press, 585--591, 2002.

\bibitem{Boot2003} Boothby, W.M.
\newblock: An Introduction to Differential Manifolds and Riemannian Geometry. 
\newblock {\em . Academic Press}, London, 2003.


\bibitem{Tene2000} Tenenbaum, J,  De Silva, V and Langford, J. 
\newblock A global geometric framework for nonlinear dimension reduction.
\newblock {\em Science}, vol. 290, 2000.

\bibitem{Roweis2000} Roweis ST and Saul LK.
\newblock  Nonlinear dimensionality reduction by locally linear embedding.
\newblock {\em Science}, 290:2323–2326, 2000.

\bibitem{Cox2000} Cox, Trevor and Cox, Michael.
\newblock Multidimensional Scaling.
\newblock {\em  Second Edition. Chapman \& Hall/CRC}, September 2000.

\bibitem{Lind2015} Lindenbaum, Ofir and Yeredor, Arie and Salhov, Moshe and Averbuch, Amir.
\newblock MultiView Diffusion Maps.
\newblock {\em CoRR}.
\newblock \url {https://arxiv.org/pdf/1508.05550.pdf}, 2015.

\bibitem{Cama2016} Camastra, Francesco and Staiano, Antonino.
\newblock  Intrinsic dimension estimation: Advances and open problems.
\newblock {\em Inf. Sci.},328,C, 26-41, 2016.

\bibitem{Lev2005} Levina, Elizaveta  and Bickel, Peter.
\newblock  Maximum Likelihood Estimation of Intrinsic Dimension.
\newblock {\em Advances in Neural Information Processing Systems 17},777--784, MIT Press, 2005.

\bibitem{Pime2014} Pimentel, Marco, Clifton, David, Clifton,  Lei  and 
Tarassenko, Lionel.
\newblock   A review of novelty detection.
\newblock {\em Signal Processing}, 99:215–249, 2014.

\bibitem{Gal2013} Mishne, Gal and Cohen, Israel.
\newblock Multiscale Anomaly Detection Using Diffusion Maps.
\newblock {\em IEEE Journal of Selected Topics in Signal Processing}, Vol. 7, No. 1, 2013.

\bibitem{Gold2016} Goldstein, Markus and Uchida, Seiichi.
\newblock A Comparative Evaluation of Unsupervised Anomaly Detection Algorithms for Multivariate Data.
\newblock {\em PLOS ONE}, DOI:10.1371/journal.pone.0152173, 2016.

\bibitem{LeCun1998} LeCun Y, Bottou L, Bengio Y and Haffner P.
\newblock Gradient-based learning applied to document recognition.
\newblock {\em Proceedings of the IEEE}, 86:2278–2324, 1998.


\bibitem{Lean2008} Leandro, Fernandes and Manuel, Oliveira.
\newblock Real-time line detection through an improved Hough transform voting scheme.
\newblock {\em Pattern Recognition}, Volume 41, Issue 9, September 2008.


\bibitem{Van2008} van der Maaten, L and Hinton, GE.
\newblock Visualizing High-Dimensional Data Using t-SNE.
\newblock {\em Journal of Machine Learning Research }, Volume 9, 2579-2605, 2008.


\bibitem{Ah2010}Ahranjany, S.S, Razzazi, F and Ghassemian, G.H.
\newblock A very high accuracy handwritten character recognition system for Farsi/Arabic digits using Convolutional Neural Networks. 
\newblock {\em 2010 IEEE Fifth International Conference on Bio-Inspired Computing: Theories and Applications (BIC-TA)}, pp. 1585-1592, Changsha, 2010.

\bibitem{Stein2008} Steinwart, Ingo  and Christmann, Andreas.	
\newblock Support Vector Machines.
\newblock {\em  Springer Publishing Company, Incorporated }, 2008.

\bibitem{Babu2014} Babu, U.R, Venkateswarlu, Y and Chintha, A.K.	
\newblock Handwritten Digit Recognition Using K-Nearest Neighbour Classifier.
\newblock {\em  2014 World Congress on Computing and Communication Technologies},  pp. 60-65, Trichirappalli, 2014.






\end{thebibliography}
