% Chapter 6
\chapter{Conclusion} % Main chapter title

\label{Chapter6} % Fr referencing the chapter elsewhere, use \ref{Chapter1} 

\lhead{Chapter 6. \emph{Conclusion}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------

\section{Conclusions}

\begin{enumerate}
\item Deviating from primary evaluation methodology of manifold leaning algorithms based on artificial data sets, we use MNIST datasets for optical character recognition.
\item The out of sample prediction for manifold algorithms indicates that test points are projected on the corrects clusters of training datasets, but separation of some numbers were blurred.
\item The preprocessing of MNIST data by manifold learning algorithms didn't improve accuracy in optical character recognition. 
\item For anomaly detection, the proposed algorithms performs well on the images which is not too contrast, but gives false positive on image which is of high resolutions.
\end{enumerate}

\section{Future Work}
\begin{enumerate}
\item When answering the questions on evaluating the results of manifold learning, we need to take in account of manifold structure and noises.
\item When there is multiple sub-manifolds of possibly different dimensionalities embedded in high dimensional complex data, it is most unlikely that the existing manifold learning approaches can discover all the interesting lower-dimensional structures. There is need to develop a hierarchical manifolds learning framework to discover a variety of the underlying low dimensional structures.
\item In optical character recognition, there is need to optimize the model when calculating accuracy. 
\item A future extension of this work would be combine  anomaly scores from the different multiscale levels into a single anomaly score. This will enable detecting anomalies of different size in an image, which this algorithms fails to address.
\end{enumerate}


%----------------------------------------------------------------------------------------
